Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-02 ms/main.tex
juvenile

Social interactions occur randomly:
two individuals with phenotype $A$ interact with probability $\hat{p}^2$, two individuals with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two individuals with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.

>>>>

Social interactions occur randomly:
two juvenile individuals with phenotype $A$ interact with probability $\hat{p}^2$, two juveniles with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two juveniles with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
